\input{preamble.tex}

\title{GlusterFS: Changing bricks without downtime or dataloss}
\author{140139}

\begin{document}

\maketitle

\abstract{From Landes~\cite{Landes:66}: The abstract is of utmost
  importance, for it is read by 10 to 500 times more people than hear or
  read the entire article. It should not be a mere recital of the subjects
  covered. Expressions such as "is discussed" and "is described" should
  never be included! The abstract should be a condensation and
  concentration of the essential information in the paper.}

\thispagestyle{empty}

\clearpage
\pagenumbering{roman}
\setcounter{page}{1}
\tableofcontents

\clearpage
\pagenumbering{arabic}

\section{Introduction}


\section{SLA/RECSPEC}

Please state why you are doing this project. Who will benefit from it? What
can the users expect in terms of stability and performance? What can be
measured so this can be a real ``Service Level Agreement''? Think carefully
about this in the beginning of the project, imagine you are doing this to
make money. To send an invoice (faktura) after project completion you have
to explain to the customer that the project has now been completed
according to what we agreed on when the project began. In other words, make
sure you are not ``just doing this for fun''.

\section{Survey of similar projects}


\section{Description of your experiment}


\section{Results and discussion}


\section{Security aspects}


\section{Conclusions}


\bibliographystyle{acmdoi}
\bibliography{template}

\end{document}
